My title

### 2024-11-27 paper/paper.qmd
fixed a rating graph in paper.qmd

summary_table %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

@@

data2 <- data %>% filter(rating > 4 )

@@

ggplot(data2, aes(x = rating, y = rating_count)) +
  geom_point() +
  geom_smooth( se =FALSE, color = "red", size = 1)

ggplot(data2, aes(x = rating, y = pages)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = 'red', size = 1)

@@

ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Pages by High Rated",
    x = "High Rated (1 = Yes, 0 = No)",
    y = "Average Pages",
    fill = "High Rated"
  ) +
  theme_minimal()

cover_counts <- data %>%
  group_by(rated_high, cover) %>%
  summarise(count = n()) %>%
  ungroup()

ggplot(cover_counts, aes(x = cover, y = count, fill = cover)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ rated_high) +
  labs(title = "Count of Hardcover and Paperback by Rated High",
       x = "Cover Type",
       y = "Count") +
  theme_minimal()

>>>>

summary_table %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
```

```{r}
#| label: summary_statistic_cleaned_dataset125
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

data2 <- data %>% filter(rating >= 4)
data3 <- data %>% filter(rating < 4)
data2 <- data2 %>% mutate(group = "High Rating (>= 4)")
data3 <- data3 %>% mutate(group = "Low Rating (< 4)")

# Combine the two datasets
combined_data <- bind_rows(data2, data3)

avg_publish_years <- combined_data %>%
  group_by(group) %>%
  summarise(avg_publish_year = mean(publish_year, na.rm = TRUE))

# Create a combined scatter plot with facets
ggplot(combined_data, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal() +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
             color = "red", linetype = "dashed", size = 1)

@@

data2 <- data %>% filter(rating >= 4)

@@

ggplot(data2, aes(x = rating, y = rating_count)) +
  geom_point()

ggplot(data2, aes(x = rating, y = pages)) +
  geom_point()

@@

ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Pages by High Rated",
    x = "High Rated (1 = Yes, 0 = No)",
    y = "Average Pages",
    fill = "High Rated"
  ) +
  theme_minimal()
```
